\Title

### 2022-09-29 Grimaldi-etal-BiolCybernetics.tex
Results: 3.3

We plot here main axis of interests. First, as we change the mean spatial frequency of the texture, we observe a montonous decrease in accuracy. This comes as a similar trend as that observed in the primary visual areas~\citep{Priebe2006}. Notably, the accuracy is better for a large spatial frequency bandwidth (which qualitatively ressemble a more textured stimuls) than for a grating-like stimulation, reminiscent to the behavioural response of humans' eye movemnts to such stimuli~\citep{Simoncini2012}. Interestingly, we also see a modulation of accuracy as a function of orientation bandwidth. When the stimulus is grating-like and that the orientation is arbitrary with respect to the direction of motion, the system is faced with the aperture problem and see a decrease of accuracy. This is not the case for isotropic stimuli or when the orientation is perpendicular to the direction of motion. Finally, we manipulated the amount of change between two successive frames, similar to a temperature parameter. This shows a progressive decrease in accuracy similar to that observed in the amplitude of humans' eye movements~\citep{MansourPour2018}.
%
\subsection{Accuracy for the motion detection task}
%%%-----------------------------------------------------------------

>>>>

We plot here main axis of interests. First, as we change the mean spatial frequency of the texture, we observe a montonous decrease in accuracy. This comes as a similar trend as that observed in the primary visual areas~\citep{Priebe2006}. \note{we should really do something more serious here...} Notably, the accuracy is better for a large spatial frequency bandwidth (which qualitatively ressemble a more textured stimuls) than for a grating-like stimulation, reminiscent to the behavioural response of humans' eye movemnts to such stimuli~\citep{Simoncini2012}. Interestingly, we also see a modulation of accuracy as a function of orientation bandwidth. When the stimulus is grating-like and that the orientation is arbitrary with respect to the direction of motion, the system is faced with the aperture problem and see a decrease of accuracy. This is not the case for isotropic stimuli or when the orientation is perpendicular to the direction of motion. Finally, we manipulated the amount of change between two successive frames, similar to a temperature parameter. This shows a progressive decrease in accuracy similar to that observed in the amplitude of humans' eye movements~\citep{MansourPour2018}.
%
\subsection{Accuracy for the motion detection task}
%%%-----------------------------------------------------------------
